NLP and NER

### 2021-10-13 NER_analysis_copy.Rmd
Complete NER Analysis

pipeline <- list(sentenceAnnotator, wordAnnotator, characterAnnotatorEN, locationAnnotatorEN)
```

@@

```{r backup_join}
write_csv(df2, "pre_join_entities.csv")
```

@@

```{r importing_entities_clean}
clean_entities <- read.csv("entities_cleaned.csv")
```

@@

```{r message=FALSE}
#create sentiment table
entities_sentiment <- entities_unnest %>%
  group_by(author, title) %>%
  inner_join(get_sentiments("nrc")) %>%
  count(sentence_nr, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```

@@

```{r message=FALSE}
ner_total_sentiment <- entities_matches_sentiment %>%
  group_by(author, title, words, kind) %>%
  summarise(total = mean(sentiment))  
```

@@

```{r message=FALSE}
ner_total_sentiment %>%
  group_by(title) %>%
  filter(kind == "person") %>%
  top_n(2) %>%
  mutate(words = reorder(words, total)) %>%
  ggplot(aes(words, y = total, fill = title)) +
  geom_col() +
  facet_wrap(~ title, scales = "free") +
  coord_flip()
```

@@

```{r radar_plot_total, message=FALSE}
radar_facet <- entities_matches_sentiment %>%
  select(-positive, -negative, -sentiment) %>% #drop out the unnecessary columns 
  group_by(title, words, kind) %>%
  summarise(across(anger:trust, sum)) %>%
  mutate(total = rowSums(across(where(is.numeric))))  %>%
  arrange(desc(total)) %>%
  head(10)  %>% #Change number to include more or fewer entities
  mutate(across(anger:trust, .fns = ~ round((. / total) * 100))) %>%
  select(-total,-kind)

@@

```{r message=FALSE}
radar_facet_sentiment <- entities_matches_sentiment %>%
  #Change filter to locations for locations
  filter(words == "Dick") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>%
  arrange(desc(sentiment))  %>%
  head(5)  %>% #Change number to include more or fewer entities
  select(-positive, -negative, -sentiment, -kind)

@@

@@

data_for_tender <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Dick"), ] %>% filter(title == "Tender is the Night") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)
temp_table <- data_for_gatsby %>% ungroup() %>% select(-title, -words)
#sum_anger <- data_for_gatsby %>% sum(anger)
data_for_gatsby_final <- mapply(sum, temp_table)

@@

ggRadar(
  data = radar_facet_sentiment_2,
  mapping = aes(color = title, facet = words),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```

>>>>

pipeline <- list(sentenceAnnotator, wordAnnotator, characterAnnotatorEN)
```

@@

```{r backup_join}
write_csv(df2, "pre_join_entities_new.csv")
```

@@

```{r importing_entities_clean}
clean_entities <- read.csv("entities_clean.csv")
```

@@

```{r message=FALSE}
#create sentiment table
entities_sentiment <- entities_unnest %>%
  group_by(author, title) %>%
  inner_join(get_sentiments("nrc")) %>%
  count(sentence_num, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```

@@

```{r message=FALSE}
ner_total_sentiment <- entities_matches_sentiment %>% drop_na(words) %>%
  group_by(author, title, words, kind) %>%
  summarise(total = mean(sentiment))  
```

@@

```{r message=FALSE}
ner_total_sentiment %>%
  group_by(title) %>%
  filter(kind == "person") %>%
  top_n(5) %>%
  mutate(words = reorder(words, total)) %>%
  ggplot(aes(words, y = total, fill = title)) +
  geom_col() +
  facet_wrap(~ title, scales = "free") +
  coord_flip()
```

@@

```{r radar_plot_total, message=FALSE}
radar_facet <- entities_matches_sentiment %>% drop_na(words) %>%
  select(-positive, -negative, -sentiment) %>% #drop out the unnecessary columns 
  group_by(title, words, kind) %>%
  summarise(across(anger:trust, sum)) %>%
  mutate(total = rowSums(across(where(is.numeric))))  %>%
  arrange(desc(total)) %>%
  head(10)  %>% #Change number to include more or fewer entities
  mutate(across(anger:trust, .fns = ~ round((. / total) * 100))) %>%
  select(-total,-kind)

@@

```{r message=FALSE}
radar_facet_sentiment <- entities_matches_sentiment %>%
  #Change filter to locations for locations
  filter(kind == "person") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>%
  arrange(desc(sentiment))  %>%
  head(10)  %>% #Change number to include more or fewer entities
  select(-positive, -negative, -sentiment, -kind)

@@

data_for_gatsby <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, c("Gats", "Jay")), ] %>% filter(title == "The Great Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

new_gatsby <- data_for_gatsby[c(1:3),c(3:10)] %>%  summarise(across(anger:trust, sum)) %>% mutate(protagonist = "Gatsby", .before  = anger)
new_gatsby_sum <- bind_rows(data_for_gatsby, new_gatsby)

data_for_diver <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Dick"), ] %>% filter(title == "Tender is the Night") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

data_for_anthony <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Antho"), ] %>% filter(title == "The Beautiful and Damned") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

data_for_amory <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Amor"), ] %>% filter(title == "This Side of Paradise") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

@@

data_for_daisy <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Dais"), ] %>% filter(title == "The Great Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

data_for_gatsby_2 <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Jay"), ] %>% filter(title == "The Great Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

data_for_henry <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Cath"), ] %>% filter(title == "A Farewell to Arms") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

temp_table1 <-bind_rows(data_for_gatsby, data_for_gatsby_2) %>% ungroup() %>% select(-title, -words)
temp_table2 <- data_for_diver %>% ungroup() %>% select(-title, -words)
temp_table3 <- data_for_anthony %>% ungroup() %>% select(-title, -words)
temp_table4 <- data_for_amory %>% ungroup() %>% select(-title, -words)
temp_table5 <- data_for_daisy %>% ungroup() %>% select(-title, -words)
temp_table6 <- data_for_henry %>% ungroup() %>% select(-title, -words)
#sum_anger <- data_for_gatsby %>% sum(anger)
data_for_gatsby_final <- mapply(sum, temp_table1)
data_for_diver_final <- mapply(sum, temp_table2)
data_for_anthony_final <- mapply(sum, temp_table3)
data_for_amory_final <- mapply(sum, temp_table4)
data_for_daisy_final <- mapply(sum, temp_table5)
data_for_henry_final <- mapply(sum, temp_table6)

protag_fitz <- read_csv("protag_f.csv") %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))
Gatsby_scale <- protag_fitz %>% filter(protagonist == "Gatsby")

@@

ggRadar(
  data = protag_fitz %>% select(-total),
  mapping = aes(color = protagonist, facet = protagonist),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```
